The ANthropological Notation Ontology (ANNO): A core ontology for annotating human bones and deriving phenotypes

### 2023-09-07 paper.tex
start example for resolving incongruities

\subsection{Validation}
When transforming the input sheet to ANNOds, SMOG~\citep{smog} executes some basic validation heuristics, such as warning on undefined references.
\todo{pyshacl}

>>>>

%\subsection{Validation}
%When transforming the input sheet to ANNOds, SMOG~\citep{smog} executes some basic validation heuristics, such as warning on undefined references.
%\todo{pyshacl}

\subsection{Resolving incongruities}
The domain experts reconciled conflicting literature arrive at a consistent and logical result.
As an example, the \emph{Corpus ossis pubis} (pubic body) forms the proximal part of the Os pubis and includes the anterior part of the Acetabulum as well as the Eminentia iliopubica, which is a small elevation on the Corpus ossis pubis.
%An example of addressing incongruities was the definition of the Corpus ossis pubis. Redefined from ANNO by SO_OO53.
%It is important to emphasize that the definition of the Corpus ossis pubis varies in the literature.
According to the TA and others~\citep{ta2,schemamann,anatomylexicon2007,drake2019gray,anatomylexicon,prometheus2,anatomie}, this landmark is located in the region of the Facies symphysialis, which is defined here as the Pars symphysialis.
Since the \emph{Corpi of the Os ischii} and \emph{Os ilii} are located in the area of the \emph{Acetabulum}, it is logical to place the \emph{Corpus ossis pubis} in this region as well (see references 6, 14, 24, 31, 54), thereby forming the Acetabulum from all Corpi (Corpus ossis ilii, Corpus ossis ischii, and Corpus ossis pubis).
The Pars symphysialis ossis pubis has ventral-medially the Facies symphysialis, which connects the paired Ossa pubes of the pelvic bones.
In the Pars symphysialis, the Ramus inferior ossis pubis and Ramus superior ossis pubis merge into each other.
This landmark represents a redefinition. In the literature, this landmark is often referred to as the Corpus ossis pubis (see references 1, 10, 12, 13, 15, 18, 21, 22).
However, other sources (see references 6, 14, 24, 31, 54), as well as this one, place the Corpus ossis pubis in the region of the Acetabulum (see the definition of the Corpus ossis pubis).
This redefinition closes the resulting gap in the definition of the area between the Ramus inferior ossis pubis and the Ramus superior ossis pubis.
